### 2018-02-28 analysis_code/agents_table.Rmd
tweaks

```{r echo=FALSE,message=FALSE}

@@

concise_rep <- function(alg) {
  if (alg == "ThompsonSampling") {
    return("TS")
  } else if (alg == "DynamicEpsilonGreedy") {
    return("DEG")
  } else if (alg == "DynamicGreedy") {
    return("DG")
  }
}

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy")
print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (prior in priors) {
  for (j in 1:length(time_horizons)) {
    results <- matrix(nrow=length(agent_algs), ncol=length(algs))
    colnames(results) <- c(paste(concise_rep(alg_pairs[1]), concise_rep(alg_pairs[2]), sep=" vs "), paste(concise_rep(alg_pairs[3]), concise_rep(alg_pairs[4]), sep=" vs "), paste(concise_rep(alg_pairs[5]), concise_rep(alg_pairs[6]), sep=" vs "))
    rownames(results) <- agent_algs
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=2)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=2)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=2)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares_percent, "%")
        }
      }
      tab <-xtable(results, caption=paste("Results for", time, prior))
      print(tab, type="html")
  }
  print('<br><br><br><br><br><br>')
  }

>>>>

 <style>
   th,td{
     padding:10px;
   }
 </style>
```{r echo=FALSE,message=FALSE}

@@

concise_alg_rep <- function(alg) {
  if (alg == "ThompsonSampling") {
    return("TS")
  } else if (alg == "DynamicEpsilonGreedy") {
    return("DEG")
  } else if (alg == "DynamicGreedy") {
    return("DG")
  }
}

concise_agent_rep <- function(agent_alg) {
  if (agent_alg == "HardMax") {
    return("HM")
  } else if (agent_alg == "HardMaxWithRandom") {
    return("HMR")
  } else if (agent_alg == "SoftMax") {
    return("SM")
  }
}

get_agent_rep <- function(repre) {
  res <- c()
  for(a in repre) {
    res <- c(res, concise_agent_rep(a))
  }
  return(res)
}

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy")
print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (prior in priors) {
  for (j in 1:length(time_horizons)) {
    results <- matrix(nrow=length(agent_algs), ncol=length(algs))
    colnames(results) <- c(paste(concise_alg_rep(alg_pairs[1]), concise_alg_rep(alg_pairs[2]), sep=" vs "), paste(concise_alg_rep(alg_pairs[3]), concise_alg_rep(alg_pairs[4]), sep=" vs "), paste(concise_alg_rep(alg_pairs[5]), concise_alg_rep(alg_pairs[6]), sep=" vs "))
    rownames(results) <- get_agent_rep(agent_algs)
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=2)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=2)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=2)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares_percent, "%")
        }
      }
      tab <-xtable(results, caption=paste("Results for", time, prior))
      print(tab, type="html")
  }
  print('<br><br><br><br><br><br>')
  }
